Progress report: \textit{Emys marmorata} sub-species identification and classification

### 2013-04-03 documents/turtle_report.Rnw
most maps done. model resamp dist plots done.

<<>>=
map <- map_data('state')
st <- c('california', 'oregon', 'washington')
map <- map[map$region == st, ]
@

@@

<<dac-geo, eval = TRUE>>=
#ggdac <- map.plot(data = turtle.info
#                  , label = tmorph.dac
#                  , map = map
#                  )
@

@@

% classification results
% not necessary to show tables
% just use maps and mark which are misclassified
%   make train tiny dots and test large dots
%   misclassified are a different shape

>>>>

<<>>=
map <- map_data('state')
st <- c('california', 'oregon', 'washington')
map <- map[map$region == st, ]

turtle.train <- lapply(turtle.train, 
                       function(x) {
                         x$long <- as.numeric(as.character(x$long)) * -1
                         x$lat <- as.numeric(as.character(x$lat))
                         x})
turtle.test <- lapply(turtle.test,
                      function(x) {
                        x$long <- as.numeric(as.character(x$long)) * -1
                        x$lat <- as.numeric(as.character(x$lat))
                        x})

labs <- Map(function(x, n) x[, n],
            x = turtle.train, n = names(turtle.train))
@

@@

<<dac-geo, eval = FALSE>>=
# map is the map of cali, ore, wash

#ggdac <- map.plot(data = turtle.info
#                  , label = tmorph.dac
#                  , map = map
#                  )
@

@@

In the interest of space/time, I'm only going to display results from one of the selected models from each method for each classification scheme.

<<multi-map, eval = FALSE>>=
tm.map <- mapply(class.map
                 , train = turtle.train
                 , test = turtle.test
                 , label = labs
                 , pred = tm.class
                 , MoreArgs = list(map = map)
                 , SIMPLIFY = FALSE)
tm.map
@

<<nnet-map, eval = FALSE>>=
tnn.class.tiny <- lapply(tnn.class, function(x) x[[1]])
tnn.map <- mapply(class.map
                 , train = turtle.train
                 , test = turtle.test
                 , label = labs
                 , pred = tnn.class.tiny
                 , MoreArgs = list(map = map)
                 , SIMPLIFY = FALSE)
tnn.map
@

<<rf-map, eval = FALSE>>=
trf.class.tiny <- lapply(trf.class, function(x) x[[1]])
trf.map <- mapply(class.map
                 , train = turtle.train
                 , test = turtle.test
                 , label = labs
                 , pred = trf.class.tiny
                 , MoreArgs = list(map = map)
                 , SIMPLIFY = FALSE)
trf.map
@

I'm currently holding back on showing the tables because there are a lot of them.

But I can show the comparison of the predictive accuracies.

<<resamp, eval = FALSE>>=
tmod.re.clean <- lapply(tmod.re, function(x) clean.resamp(x$values))
tmod.re.gg <- lapply(tmod.re.clean, resamp.plot)
tmod.re.gg
@
